Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-03 bbbq_article.tex
Improvements by @fransbianchi

Epitope prediction is important to understand the immune system 
and for the design of vaccines.
In this study, we provide evidence that epitopes
derived from TMHs are a major but overlooked source of MHC epitopes. 
Our bioinformatics predictions indicate that the TMH-derived epitope repertoire is larger than expected by chance, 
regardless of the organism. Furthermore we see despite the bias towards hydrophilic peptides due to their enhanced ionization in mass spec that in several peptide elution studies still a higher fraction of TMH derived epitopes is found than predicted by chance. Therefor it's tempting to assume that this would also result in enhanced T-cell responses, assuming that the conservation of TMH's across organisms does not effect the deletion of such T-cells by central tolerance mechanisms.
Moreover, reanalysis of peptide elution studies confirmed the presentation of TMH-derived epitopes.
Finally, our SNP analysis shows that TMHs are evolutionary more conserved 
than solvent-exposed protein regions.

@@

Although our data show that 
TMH-derived epitopes are presented in MHC-I and MHC-II, 
the molecular mechanisms of how integral membrane proteins are processed 
for MHC presentation are largely unknown \cite{bianchi2017}. 
Most prominently, the fundamental principles of 
how TMHs are extracted from their hydrophobic lipid environments 
into the aqueous vacuolar lumen, 
and their prior or subsequent proteolytic processing are unresolved.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{T cells recognize different protein regions than B cells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \paragraph{Over-presentation in silico}
Although it's well known that T cells and B Cells seem to predominantly recognize different protein regions,
this is enhanced by the over-presentation of TMH-derived epitopes, as TMH's buried in the lipid bilayer are unlikely to be recognized by BCR's.

>>>>

Epitope prediction is important to understand the immune system 
and for the design of vaccines.
In this study, we provide evidence that epitopes
derived from TMHs are a major but overlooked source of MHC epitopes. 
Our bioinformatics predictions indicate that the TMH-derived epitope repertoire is larger than expected by chance, 
regardless of the organism. Furthermore we see despite the bias towards hydrophilic peptides due to their enhanced ionization in mass spec that in several peptide elution studies still a higher fraction of TMH derived epitopes is found than predicted by chance. Therefor it's tempting to assume that this would also result in enhanced T-cell responses, assuming that the conservation of TMH's across organisms does not significantly effect the deletion of such T-cells by central tolerance mechanisms.
Moreover, reanalysis of peptide elution studies confirmed the presentation of TMH-derived epitopes.
Finally, our SNP analysis shows that TMHs are evolutionary more conserved 
than solvent-exposed protein regions.

@@

Although our data show that 
TMH-derived epitopes are presented in all classical MHC-I and MHC-II haplotypes, 
the molecular mechanisms of how integral membrane proteins are processed 
for MHC presentation are largely unknown \cite{bianchi2017}. 
Most prominently, the fundamental principles of 
how TMHs are extracted from their hydrophobic lipid environments 
into the aqueous vacuolar lumen, 
and their prior or subsequent proteolytic processing are unresolved.

@@
